The pollination trade-off

### 2018-12-01 paper/manuscript.Rmd
Fix typos results

We first examined the relationship between the heterospecific and conspecifi  pollen deposited on stigmas of a species in a community. 
We found that in a majority of cases there was either no significant relationship between heterospecific and conspecific pollen or there was a negative relationship (Figure \@ref(fig:fig-trade-off-predictions)a). 
Although the overall relationship between between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively). 
This large variation among species was accompained by moderate variation within species (for those sampled in multiple communities). 
Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others. 
Furthermore, although neither a positive or negative relationship was dominant, we found that, in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs. facilitation at the community level**. (a) Some species experience more competition for pollination than others. Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities. Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome. The number of of plants analised for each species is shown within brakets next to the species name. (b) Despite the variety of slopes, overall plants had have more conspecific than heterospecific pollen deposited in their stigmas. (c) Generally, plants also had more pollen depositied in their stigmas when they were open to animal-mediated pollination than when they were closed. However in the majority of cases the difference is not large enough to be statistically significant at the 0.05 level. In all plots, erro bars correspond to ± the standard error (SE)."}
# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```

@@

We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
We found that, generally most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.

>>>>

We first examined the relationship between the heterospecific and conspecific pollen deposited on stigmas of a species in a community. 
We found that in a majority of cases there was either no significant relationship between heterospecific and conspecific pollen or there was a negative relationship (Figure \@ref(fig:fig-trade-off-predictions)a). 
Although the overall relationship between heterospecific and conspecific pollen was positive (Supp info Table XX), the number of species in their communities with a positive relationship was slightly smaller to those with a negative relationship (`r counts_facilitation_slope$np[3]`% and `r counts_facilitation_slope$np[1]`% respectively). 
This large variation among species was accompanied by moderate variation within species (for those sampled in multiple communities). 
Indeed, `r numbers2words(nrow(sp_both_pos_neg))` species  (*Cypella herbertii*, *Diplotaxis tenuifolia*, *Hirschfeldia incana*, and *Carduus acanthoides*) showed significantly positive relationships in some communities and negative in others. 
Furthermore, although neither a positive or negative relationship was dominant, we found that in almost all cases, more conspecific than heterospecific pollen was deposited on stigmas (Figure \@ref(fig:fig-trade-off-predictions)b).

```{r fig-trade-off-predictions, fig.height= 4, fig.width = 6.5, fig.cap = "**Competition vs. facilitation at the community level**. (a) Some species experience more competition for pollination than others. Points indicate the estimated slopes for the relationship between the amount of heterospecific and conspecific pollen deposited per stigma across species in their communities. Negative slopes indicate that plants experience competition for animal-mediated pollination, while positive slopes indicate that facilitation is the predominant outcome. The number of plants analysed for each species is shown within brackets next to the species name. (b) Despite the variety of slopes, overall plants had more conspecific than heterospecific pollen deposited in their stigmas. (c) Generally, plants also had more pollen deposited in their stigmas when they were open to animal-mediated pollination than when they were closed. However, in the majority of cases, the difference is not large enough to be statistically significant at the 0.05 level. In all plots, error bars correspond to ± the standard error (SE)."}
# fig_random_slopes <- plot_random_slopes(facilitation_random_effects, dep_frame)
# fig_con_con <- plot_bagged_vs_open_conspecific(dep_frame)
# fig_hetero_con <- make_fig_con_hetero_empirical(dep_frame)
# pdf(width = 6.5, height = 4)
drake::loadd(fig_random_slopes)
drake::loadd(fig_con_con)
drake::loadd(fig_hetero_con)
width_left <- 6.5*3/5
bar_plot_width <- 0.325
rw <- c(width_left - bar_plot_width,
        bar_plot_width, 
        6.5 - width_left - bar_plot_width,
        bar_plot_width)
left <- cowplot::plot_grid(
  fig_hetero_con,
  NULL,
  fig_con_con[[1]],
  fig_con_con[[2]],
  ncol = 2, 
  rel_widths = rw[c(3,4)], 
  align = "h"
)
right <- cowplot::plot_grid(
  fig_random_slopes[[1]],
  fig_random_slopes[[2]], 
  ncol = 2, 
  align = "h", 
  rel_widths = rw[1:2]
)
cowplot::plot_grid(
  right,
  left,
  ncol = 2,
  rel_widths = c(sum(rw[1:2]), sum(rw[3:4]))
)
# dev.off()
```

@@

We then compared the amount of conspecific pollen deposited on flowers open to animal-mediated pollinators and those that were closed. 
We found that generally, most species had more conspecific pollen deposited in their stigmas when animal-mediated pollination took place, although for most species the difference was not significant at the 0.05 level (Mann-Withney U tests; Figure \@ref(fig:fig-trade-off-predictions)c). 
Specifically, the difference weas non-signifcant for `r sp_con_con$np[sp_con_con$effect_category == "neutral"]`% of species in a community, `r sp_con_con$np[sp_con_con$effect_category == "positive"]`% had significantly more pollen when open, and the remaining `r sp_con_con$np[sp_con_con$effect_category == "negative"]`% had significantly less pollen when open.
